### 2019-03-27 Introduction.tex
Updates from Overleaf

 To apply RNNs to multi-label problems, one has to map the given set of labels $\mathbf{y}$ to a sequence $\mathbf{s}=(s_1,s_2,...,s_T)$, on training documents. This is usually obtained by writing the label set in a globally fixed order (e.g.\ by label frequency), similar to PCC.
 % After mapping the ground truth set $\mathbf{y}^{(n)}$ to a sequence $\mathbf{s}^{(n)}$ with the chosen order for each training instance $(x^{(n)},\mathbf{y}^{(n)})$,
 Once mapping is done, RNN are trained with the standard maximum likelihood objective \cite{DBLP:conf/nips/NamMKF17}: 
\begin{align}
\maximize \sum_{n=1}^N \log p(\mathbf{s}^{(n)}|x^{(n)})
\label{eq:standard_rnn}
\end{align}
\kechen{where $N$ is the total number of samples in the corpus and $n$ represents the $n$-th sample.} \newcite{vinyals2015order} proposes to dynamically choose during training the sequence order deemed as most probable by the current RNN model:
\begin{align}
\maximize \sum_{n=1}^N \max_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})}\log p(\mathbf{s}|x^{(n)})
\label{eq:max_obj}
%\vspace{-2ex}
\end{align}
where the $\pi(\mathbf{y}^{(n)})$ stands for all  permutations of $\mathbf{y}^{(n)}$. This eliminates the need to manually specify label order.
However, as noticed by the authors, this objective cannot be used in the early training stages: the early order choice (often random) is reinforced by this objective and can be stuck upon permanently. To address this issue, \newcite{vinyals2015order}~also proposes two smoother alternative objectives to initialize the model training:

>>>>

 To apply RNNs to multi-label problems, one has to map the given set of labels $\mathbf{y}$ to a sequence $\mathbf{s}=(s_1,s_2,...,s_T)$, on training documents. This is usually obtained by writing the label set in a globally fixed order (e.g.\ by label frequency), similar to PCC.
 % After mapping the ground truth set $\mathbf{y}^{(n)}$ to a sequence $\mathbf{s}^{(n)}$ with the chosen order for each training instance $(x^{(n)},\mathbf{y}^{(n)})$,
 Once mapping is done, RNN are trained with the standard maximum likelihood objective \cite{DBLP:conf/nips/NamMKF17}: 
\begin{align}
\maximize \sum_{n=1}^N \log p(\mathbf{s}^{(n)}|x^{(n)})
\label{eq:standard_rnn}
\end{align}
\kechen{where $N$ is the total number of documents in the corpus and $n$ represents the $n^{\text{th}}$ document.} \newcite{vinyals2015order} proposes to dynamically choose during training the sequence order deemed as most probable by the current RNN model:
\begin{align}
\maximize \sum_{n=1}^N \max_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})}\log p(\mathbf{s}|x^{(n)})
\label{eq:max_obj}
%\vspace{-2ex}
\end{align}
where the $\pi(\mathbf{y}^{(n)})$ stands for all  permutations of $\mathbf{y}^{(n)}$. This eliminates the need to manually specify label order.
However, as noticed by the authors, this objective cannot be used in the early training stages: the early order choice (often random) is reinforced by this objective and can be stuck upon permanently. To address this issue, \newcite{vinyals2015order}~also proposes two smoother alternative objectives to initialize the model training:

### 2019-03-27 Model.tex
Updates from Overleaf

>>>>

\kechen{The reviewer is correct in that our method takes more time than vanilla-RNN, in fact by a factor of 1.5*K. "K" because there are K permutations for each datapoint, and 1.5 (approximatively) because each epoch requires one more forward pass. However, the comparisons done in the paper against state of the art RNN, are fair on performance and run time: the baselines also use K* more permutations per datapoint, so compare to these our methosd is only 1.5 (or so) slower.}
